---
title: "Causal Effect"
format: html
execute:
  echo: false
---

```{r}
#| label: setup
#| message: false

library(tidyverse)
library(primer.data)
library(brms)
library(tidybayes)
library(gtsummary)
```

```{r}
#| label: load data

ch6 <-
  trains |>
    select(att_end, treatment)
```

```{r}
#| label: model
#| cache: true

fit_gauss <- 
  brm(formula = att_end ~ treatment,
    data = ch6,
    family = gaussian(),
    refresh = 0,
    silent = 2,
    seed = 9)


```

```{r}
#| label: table regression

tbl_regression(fit_gauss)
```

```{r}
ndata <- tibble(treatment = c("Treated", "Control"))

model <-
fit_gauss |>
  add_epred_draws(newdata = ndata)

fit_gauss |>
  add_epred_draws(newdata = ndata) |>
  select(treatment, .draw, .epred) |>
  pivot_wider(id_cols = .draw, names_from = treatment, values_from = .epred) |>
  mutate(causal_effect = Treated - Control) |>
  select(- .draw) |>
  ggplot(aes(x = causal_effect)) +
  geom_histogram(aes(y = after_stat(count / sum(count))), bins = 100) +
  scale_y_continuous(labels = scales::percent_format()) +
  theme_classic() +
  labs(title = "Posterior for Average Treatment Effect",
       subtitle = "Exposure to Spanish-speakers shifts immigration attitudes rightward",
       x = "Difference in Attitude",
       y = "Probability")
```

The posterior, or the coefficient of Control is centered around −1.5 with a 95% Confidence Interval between −2.5 and −0.5.

The question is: What is the average treatment effect, of exposing people to Spanish-speakers, on their attitudes toward immigration? I have loaded the data, considered validity, stability, representativeness, and unconfoundedness. One problem is that politics might have changed throughout this time. I then made bayesian regression model of the end attitude to the treatment. I used add epred draws and subtracted the control from the treatment to get the causal effect. I then plotted a histogram of the causal effect
